### 2023-10-17 2.State/ai.tex
Saved figure
Changed desciption
Added one sentence
Bigger figure
Correction

\acf{AI} is very popular, and is getting more attention, being used as selling point by lots of services, the word is thrown around so much that it lost its meaning. So what are \acp{AI} exactly.

@@

The most commonly used type of \ac{AI} is machine learning, which consists of teaching the software to make decision. It is defined as the use and development of computer systems that are able to learn and adapt without following explicit instructions, by using algorithms and statistical models to analyse and draw inferences from patterns in data.

@@

%TODO add superbe diagram

>>>>

\acf{AI} is very popular, and is getting more attention, being used as selling point by lots of services, the word is thrown around so much that it has lost its meaning. So what are \acp{AI} exactly.

@@

The most promising type of \ac{AI} is machine learning, which consists of teaching the software to make decision. It is defined as the use and development of computer systems that are able to learn and adapt without following explicit instructions, by using algorithms and statistical models to analyse and draw inferences from patterns in data.

@@

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth]{ml.svg}
  \caption{Machine learning and its subsets}
  \label{fig:ml}
\end{figure}

\Cref{fig:ml} is a visual representation of machine learning and all the disciplines of machine learning. The thesis will focus, as the title implies, on the \aclp{RNN}.
